---
title: "National Health Survey Logical Regression Analysis"
author: "Sean F. Larsen"
date: "December 28, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(effects)
```

## The National Health Interview Survey
The National Health Interview Survey data comes from the CDC website.
<https://www.cdc.gov/nchs/nhis/index.htm>  
The National Health Interview Survey (NHIS) has monitored
the health of the nation since 1957. NHIS data on a broad
range of health topics are collected through personal
household interviews. For over 50 years, the U.S. Census
Bureau has been the data collection agent for the National
Health Interview Survey. Survey results have been
instrumental in providing data to track health status,
health care access, and progress toward achieving national
health objectives.  

## Load the National Health Interview Survey data
This code will load the data NatHealth2011.rds

```{r echo=FALSE}
NH11 <- readRDS("NatHealth2011.rds")
labs <- attributes(NH11)$labels
```

## Probability of Being Diagnosed with Hypertension Based on Age, Sex, Sleep, and BMI
This code is to predict the probability of being diagnosed with hypertension based on age, sex, sleep, and bmi.
First we are going to check stucture of the hypev field (Hyper Tension question), check the levels of hypev field,
collapse all missing values to NA, and run a regression model.

```{r echo=FALSE}
str(NH11$hypev)
levels(NH11$hypev)
NH11$hypev <- factor(NH11$hypev, levels=c("2 No", "1 Yes"))
hyp.out <- glm(hypev~age_p+sex+sleep+bmi,
              data=NH11, family="binomial")
coef(summary(hyp.out))
```

## Logistic regression coefficients
Generalized linear models use link functions, so raw coefficients are
difficult to interpret. For example, the age coefficient of .06 in the
model tells us that for every one unit increase in age, the
log odds of hypertension diagnosis increases by 0.06. Since most of us
are not used to thinking in log odds this is not too helpful!
One solution is to transform the coefficients to make them easier to interpret.

```{r echo=FALSE}
hyp.out.tab <- coef(summary(hyp.out))
hyp.out.tab[, "Estimate"] <- exp(coef(hyp.out))
hyp.out.tab
```

## Generating predicted values
In addition to transforming the log-odds produced by `glm' to odds, we
can use the `predict()' function to make direct statements about the
predictors in our model.  For example, we can ask "How much more likely
is a 63 year old female to have hypertension compared to a 33 year old
female?".  This will Create a dataset with predictors set at desired levels
predict hypertension at those levels.

```{r echo=FALSE}
predDat <- with(NH11,
                expand.grid(age_p = c(33, 63),
                            sex = "2 Female",
                            bmi = mean(bmi, na.rm = TRUE),
                            sleep = mean(sleep, na.rm = TRUE)))
cbind(predDat, predict(hyp.out, type = "response",
                       se.fit = TRUE, interval="confidence",
                       newdata = predDat))
```

I hve loaded the effects package to
compute quantities of interest for us (cf. the Zelig package).

```{r echo=FALSE}
plot(allEffects(hyp.out))
```

## Comparing Models
Useing the NH11 data set, I will use glm to conduct a logistic regression to predict ever worked
(everwrk) using age (age_p) and marital status (r_maritl).
Then Predict the probability of working for each level of marital status.

```{r echo=FALSE}
str(NH11$everwrk)
levels(NH11$everwrk)
NH11$hypev <- factor(NH11$hypev, levels=c("2 No", "1 Yes"))
hyp.out2 <- glm(everwrk~age_p+r_maritl,
              data=NH11, family="binomial")
coef(summary(hyp.out2))

plot(allEffects(hyp.out2))
```
